---
title: "Homework 6"
author: Tu  Nguyen
output: 
  github_document:
    pandoc_args: --webtex
  
---

This is my solution to HW6.

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
library(modelr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2

Load and clean birth weight dataset
```{r}
birthweight_df = 
  read.csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
```

From my knowledge, the mother's age and pre-pregnancy BMI can be the determinants of the baby's birth weight. 
I am interested in investigating the relationship between the mother's physique at delivery + the baby's gender and baby's birth weight. 


```{r}
proposed_model = lm(bwt ~ babysex + momage + ppbmi, data = birthweight_df)

```


Plot of model residuals against fitted values

```{r}
birthweight_df %>% 
  add_predictions(proposed_model) %>% 
  add_residuals(proposed_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```


Automate the CV process

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100)
```

Compare my model to two others 

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    proposed_mod = map(train, ~lm(bwt ~ babysex + momage + ppbmi, data = .x)),
    main_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    three_way_mod = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_proposed = map2_dbl(proposed_mod, test, ~rmse(model = .x, data = .y)),
    rmse_main = map2_dbl(main_mod, test, ~rmse(model = .x, data = .y)),
    rmse_three_way = map2_dbl(three_way_mod, test, ~rmse(model = .x, data = .y))
  )
```

Make comparison in terms of the cross-validated prediction error

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

The proposed model has the highest prediction error. Model with the head circumference, length, sex, and all interactions (including the three-way interaction) has the lowest prediction error. 


## Problem 3

Download dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Create 5000 bootstrap samples

```{r}
bootstrap_df = 
  weather_df %>% 
  bootstrap(n = 5000)
```

Find and plot the distributions of $\hat{r}^2$ and $log(\hat\beta_0 * \hat\beta_1)$


```{r}
sample_df = 
  bootstrap_df %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    r_hat_distribution = map(models, broom::glance),
    log_distribution = map(models, broom::tidy)
  ) %>% 
  select(-strap, -models)
```

 $\hat{r}^2$ plot
```{r}
r_df = 
  sample_df %>% 
  unnest(r_hat_distribution)

r_df %>% 
  ggplot(aes(x = r.squared)) + 
  geom_density()
```

Based on the plot above, the distribution of $\hat{r}^2$ is relatively normal 

Identify the 2.5% and 97.5% quantiles
```{r}
unname(quantile(pull(r_df, r.squared), 0.025))
unname(quantile(pull(r_df, r.squared), 0.975))
```
Based on the code chunk above, the 95% confidence interval for $\hat{r}^2$ is (0.893591, 0.927841)


$log(\hat\beta_0 * \hat\beta_1)$ plot

```{r}
log_df = 
  sample_df %>% 
  unnest(log_distribution) %>% 
  pivot_wider(.id:estimate,
    names_from = term, 
    values_from = estimate) %>% 
  select(-r_hat_distribution) %>% 
  rename("intercept" = "(Intercept)") %>% 
  mutate(log_distribution = log(intercept*tmin))

log_df %>% 
  ggplot(aes(x = log_distribution)) + 
  geom_density()
```

Based on the plot above, the distribution of $log(\hat\beta_0 * \hat\beta_1)$is also normal. 

Identify the 2.5% and 97.5% quantiles
```{r}
unname(quantile(pull(log_df, log_distribution), 0.025))
unname(quantile(pull(log_df, log_distribution), 0.975))
```
Based on the code chunk above, the 95% confidence interval for $log(\hat\beta_0 * \hat\beta_1)$ is (1.9744, 2.0599)



