---
title: "Homework 5"
author: Tu  Nguyen
output: github_document
---

This is my solution to HW5.

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
library(stringr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2

Load the data from a longitudinal study that included a control arm and an experimental arm, the file names include the subject ID and arm. 

```{r}
longitudinal_path = "./data"
longitudinal_files = list.files(longitudinal_path)

longitudinal_data = 
  longitudinal_files %>% 
  purrr::map(~ read_csv(file.path(longitudinal_path, .))) %>% 
  reduce(rbind)

longitudinal_df = 
  longitudinal_data %>% 
  mutate(subject_id = as.numeric(regmatches(longitudinal_files, regexpr( "\\d+", longitudinal_files))),
         arm = substr(longitudinal_files, start = 1, stop = 3)
  ) %>% 
  relocate(arm, subject_id, everything()) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observation_values"
  ) %>% 
  mutate(arm = 
           recode(arm, 
         con = "control",
         exp = "experiment")
  )
```

The following code chunk shows the spaghetti plot displaying the observations on each subject over time. 
Over the course of 8 weeks, there were not a lot of changes in observation values in the control arm participants. However, there seemed to be an increase of observation values after week 4 in overall observation values in the experimental arm participants. 

```{r}
longitudinal_df %>% 
  ggplot(aes(x = week, y = observation_values, group = subject_id, color = arm)) + 
  geom_path()
```

## Problem 3

We first generate 5000 datasets with `n = 30`, `mu = 0`, and `sigma = 5`. 

```{r}
set.seed(5)


sim_mean_sd = function(sample_size = 30, mu = 0, sigma  = 5) {
  
  sim_data = 
    tibble(
    x = rnorm(n = sample_size , mean = mu, sd = sigma)
  )


sim_result = 
  sim_data%>% 
  summarise(
    mean = mean(x),
    t_test = t.test(x, mu = 0, alternative = "two.sided", paired = FALSE, conf.level = 0.95) %>% 
      broom::tidy() %>% 
      pull(p.value)
  )

}

```

Let's use a loop function to show the results of the t-test. 

```{r}
sim_results = 
  rerun(5000, sim_mean_sd(mu = 0)) %>% 
  bind_rows()
```

With mu = {0,1,2,3,4,5,6}

```{r}
new_results = 
  tibble(
    new_mu = c(0:6)
  ) %>% 
  mutate(
    output_lists = map(.x = new_mu, ~rerun(5000, sim_mean_sd(mu = .x))),
    estimate_df = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df)
```

The following plot below shows the proportion of times the null was rejected on the y axis and the true value of `mu` on the x axis. 

```{r}
sim_results_true_mu = 
  new_results %>% 
  mutate(
    test_results = ifelse(t_test < '0.05', 1, 0)
  ) %>% 
  group_by(new_mu) %>% 
  summarise(
    reject_p_value = sum(test_results),
    total_n = n()
  ) %>%
  mutate(power = reject_p_value / total_n) 


sim_results_true_mu %>% 
  ggplot(aes(x = new_mu, y = power)) + 
  geom_point() + 
  geom_line()
```

The plot shows that the power increases as the effect size increases. 



The following code chunk showed the average estimate of mu hat on the y-axis and the true value of mu on the x-axis

```{r}
new_results %>% 
  group_by(new_mu) %>% 
  summarise(mu_hat = mean(mean)) %>% 
  ggplot(aes(x = new_mu, y = mu_hat)) +
  geom_point() + 
  geom_line()

```

The following plot shows the average estimate of mu hat only in samples for which the null was rejected on the y-axis and the true value of mu on the x-axis

```{r}
mu_hat_rejected = 
  new_results %>% 
  filter(t_test < 0.05) %>% 
  group_by(new_mu) %>% 
  summarise(rejected_mu_hat = mean(mean))

mu_hat_rejected %>% 
  ggplot(aes(x = new_mu, y = rejected_mu_hat)) + 
  geom_point() +
  geom_line()
```

The above plots showed that the same average mu hat across tests for which the null is rejected is approximately equal to the true value of mu when after true mu = 4. That means when true mu = {4,5,6}, the null hypothesis is rejected. 










